NIRCam Flux Calibration Plan

### 2017-03-26 ms.tex
I inserted the text for the stars classified in both runs.

\clearpage
\section{Spectral Typing of Candidate Analogs}
The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
We processed the data with the standard IDL routine \texttt{hsred}\footnote{https://www.mmto.org/node/536}

We normalized the raw spectra output from \texttt{hsred} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
We fit an 8th order polynomial in log space to the flux as a function of wavelength.
It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the flux drops to low values and the fit can have zero crossings.
The resulting model (fit in linear space) results large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings.
The polynomial fit is done piecewise in 3 equally spaced regions to take on small scale curvature.

@@

>>>>

\clearpage
\section{Spectral Typing of Candidate Analogs}
The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
We processed the data with the standard IDL routine \texttt{HSRED}\footnote{https://www.mmto.org/node/536}

We normalized the raw spectra output from \texttt{HSRED} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
We fit an 8th order polynomial in log space to the flux as a function of wavelength.
It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the flux drops to low values and the fit can have zero crossings.
The resulting model (fit in linear space) results large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings.
The polynomial fit is done piecewise in 3 equally spaced regions to take on small scale curvature.

@@

Figure \ref{fig:NCFOV} shows the photometry and positions of sources after 1 pass with Hectospec/MMT and Figure \ref{fig:NCFOV2ndrun} shows after a 2nd set of observations with Hectospec/MMT.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
\includegraphics[width=.49\columnwidth]{fov_ngc2420_two_runs.pdf}
\caption{We observed additional stars with Hectospec on the MMT search for additional G2~V sources. This shows the same plot as Figure \ref{figNCFOV} after a second Hectospec fiber configuration.
{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV2ndrun}
\end{figure}
